Multiple quantum NMR in solids as a method of a determination of Wigner--Yanase skew information

### 2021-02-17 manuscript.tex
Fix typos and reference styles

\section{Introduction}
\label{sec:1}
The Wigner--Yanase skew information~\cite{1,2,3} together with the Fisher information~\cite{4,5} allow to develop the powerful methods for an investigation of entanglement, including the many--particle entanglement~\cite{6,7}.
Further investigations of the many--particle entanglement require a development of the corresponding experimental methods.
In particular, it was shown~\cite{6,8} that a low bound on the quantum Fisher information~\cite{4,5} coincides with the double second moment of the spectrum of multiple quantum (MQ) coherences.
As a result, the low bound on the quantum Fisher information can be found in MQ NMR experiments~\cite{9},
in cold--atom experiments, including Bose--Einstein condensates, ultracold atoms in cavities, and trapped ions~\cite{10,11,12,13,14}.
Using the properties of the quantum Fisher information one can obtain the number of entangled particles (spins) in the system under consideration~\cite{6} and even to find the dependence of a number of entangled spins on temperature~\cite{8}.

@@

MQ NMR methods are widely used for solving problems of quantum informatics~\cite{16,17}. The MQ NMR experiment consists of four distinct periods of time Fig.~(\ref{fig:1}): preparation $(\tau)$, evolution $(t_1)$, mixing $(\tau)$, and detection $(t_2)$~\cite{9}.
MQ NMR coherences are created by a periodic multipulse sequence, consisting of
$\pm$x-pulses, irradiating the system of the preparation period~\cite{9}.
If the inverse period of the multipulse sequence significantly exceeds the local dipolar field (in frequency units)~\cite{18}
MQ NMR dynamics can be described by the averaged nonsecular two--spin/two--quantum Hamiltonian~$H_{MQ}$~\cite{19}
%
\begin{equation} \label{eq:1}
        H_{MQ} = H^{(+2)} + H^{(-2)} , \quad
        H^{(\pm 2)} = -\frac{1}{2} \sum_{j<k} D_{jk} I_{j} ^\pm I_k^\pm,
\end{equation}
%
where $D_{jk}$ is the coupling constant between spins $j$ and $k$, and $I_{j} ^+ I_k ^-$ are the raising and lowering operators of spin $j$.
On the mixing period the spin system is irradiated by the multiple sequence with $\pm y$--pulses.
As a result, the averaged nonsecular two-spin/two quantum Hamiltonian on the mixing period equals $(-H_{MQ})$~\cite{9}.

@@

\begin{thebibliography}{20}
\bibitem{1} E.P.Wigner, M.M. Yanase, Proc.Nat.Acad.Sei. USA, 49, 910-918 (1963)
\bibitem{2} Z.Chen, Phys.Rev, A71, 052302 (2005)
\bibitem{3} S.Luo, Proc.Amer. Math.Soc.132, No.885-890 (2003)
\bibitem{4} G.Toth, I.Apellaniz, J. Phys. A47,424006 (2014)
\bibitem{5} L.Pezze, A.Smerzi, M.K. Oberthaler, R. Schmied, P.Treutlein, Rev.Mod.Phys. 90, 035005 (2018)
\bibitem{6} M.Gartner, P.Hauke, A.M.Rey, Phys.Rev.Lett. 120, 040402 (2018)
\bibitem{7} S.I.Doronin, E.B.Fel'dman, I.D.Lazarev, Phys. Rev. A100,022330 (2019)
\bibitem{8} D.Girolami, B.Yadin,Entropy 19,124 (2017)
\bibitem{9} J.Baum, M.Munowitz, A.N.Garroway, A.Pines,J.Chem.Phys. 83, 2015 (1985)
\bibitem{10} B. Swingle, G. Bentsen, M. Scheleier-Smith, P. Hayden, Phys. Rev. A94, 040302 (2010)
\bibitem{11} F.M. Cucchietti, J.Opt.Soc. Am. B27, A30 (2010)
\bibitem{12} I.D. Leroux, M.H. Schleirer-Smith, V.Vuletii, Phys.Rev.Lett. 104,
	073602 (2010)

\bibitem{13} T.Macri, A. Smerzi, L.Pezze, Phys.Rev A94, 010102 (2016)
\bibitem{14} M.Gartner, J.G.Bohnet, A.Safavi-Naini, M.L. Wall, J.J. Bollinger, A.M.Rey, Nat.Phys. 13,781 (2017)
\bibitem{15} G.A.Bochkin, S.G.Vasil'ev, S.I. Doronin, E.I.Kuznetsova,I.D.Lazarev,E.B.Fel'dman, Appl.Magn.Reson. 51,667-678 (2020)
\bibitem{16} E.B.Fel'dman, A.N. Pykov, A.I.Zenchuk, Philos. Trans. R. Soc. London A370, 4690 (2012)
\bibitem{17} G.B.Furman, V.M.Meerovich, V.L.Sokolovsky, Phys. Rev. A.78 042301 (2008)
\bibitem{18} M.Goldman. Spin temperature and nuclear magnetic resonance in solids, Oxford,UK, Clarendon Press. 1970.
\bibitem{19} S.I.Doronin, I.I.Maksimov, E.B.Fel’dman, J. Exp. Theor. Phys.91, 597 (2000)
\bibitem{20} E.B.Fel'dman, S.Lacelle,Chem.Phys.Lett. 253, 27 (1996)
\bibitem{21} A.Abragam, The Principles of Nuclear Magnetism, Clarendon. Oxford. 1961
\bibitem{22} J. Baugh, A. Kleinhammes, D. Han, Q. Wang, Y.Wu, Science 294, 1505 (2001)
\bibitem{23} G.A. Bochkin, E.B. Fel'dman, E.B. Kuznetsova, I.D. Lasarev, S.G. Vasil'ev, V.I.Volkov, J. Magn.Reson. 319, 106816 (2020)
\end{thebibliography}

>>>>

\section{Introduction}
\label{sec:1}
The Wigner--Yanase skew information~\cite{1,2,3} together with the Fisher information~\cite{4,5} allow to develop the powerful methods for an investigation of entanglement, including the many--particle entanglement~\cite{6,7}.
Further investigations of the many--particle entanglement require a development of the corresponding experimental methods.
In particular, it was shown~\cite{6,8} that a low bound on the quantum Fisher information~\cite{4,5} coincides with the double second moment of the spectrum of multiple quantum (MQ) coherences.
As a result, the low bound on the quantum Fisher information can be found in MQ NMR experiments~\cite{9},
in cold--atom experiments, including Bose--Einstein condensates, ultracold atoms in cavities, and trapped ions~\cite{10,11,12,13,14}.
Using the properties of the quantum Fisher information one can obtain the number of entangled particles (spins) in the system under consideration~\cite{6}
and even to find the dependence of the number of entangled spins on temperature~\cite{8}.

@@

MQ NMR methods are widely used for solving problems of quantum informatics~\cite{16,17}. The MQ NMR experiment consists of four distinct periods of time Fig.~(\ref{fig:1}): preparation $(\tau)$, evolution $(t_1)$, mixing $(\tau)$, and detection $(t_2)$~\cite{9}.
MQ NMR coherences are created by a periodic multipulse sequence, consisting of
$\pm$x-pulses, irradiating the system of the preparation period~\cite{9}.
If the inverse period of the multipulse sequence significantly exceeds the local dipolar field (in frequency units)~\cite{18}
MQ NMR dynamics can be described by the averaged nonsecular two--spin/two--quantum Hamiltonian~$H_{MQ}$~\cite{19}
%
\begin{equation} \label{eq:1}
        H_{MQ} = H^{(+2)} + H^{(-2)} , \quad
        H^{(\pm 2)} = -\frac{1}{2} \sum_{j<k} D_{jk} I_{j} ^\pm I_k^\pm,
\end{equation}
%
where $D_{jk}$ is the coupling constant between spins $j$ and $k$,
and $I_{j}^+, I_k ^-$ are the raising and lowering operators of spin $j$.
On the mixing period the spin system is irradiated by the multiple sequence with $\pm y$--pulses.
As a result, the averaged nonsecular two-spin/two quantum Hamiltonian on the mixing period equals $(-H_{MQ})$~\cite{9}.

@@

\begin{thebibliography}{20}
	\bibitem{1} E.P.Wigner, M.M. Yanase, Proc.Nat.Acad.Sei. USA, \textbf{49}, 910-918 (1963)
	\bibitem{2} Z.Chen, Phys.Rev.A. \textbf{71}, 052302 (2005)
  \bibitem{3} S.Luo, Proc.Amer. Math.Soc. \textbf{132}, No.885-890 (2003)
  \bibitem{4} G.Toth, I.Apellaniz, J. Phys. A. \textbf{47},424006 (2014)
  \bibitem{5} L.Pezze, A.Smerzi, M.K. Oberthaler, R. Schmied, P.Treutlein, Rev.Mod.Phys. \textbf{90}, 035005 (2018)
  \bibitem{6} M.Gartner, P.Hauke, A.M.Rey, Phys.Rev.Lett. \textbf{120}, 040402 (2018)
  \bibitem{7} S.I.Doronin, E.B.Fel'dman, I.D.Lazarev, Phys. Rev. A. \textbf{100},022330 (2019)
  \bibitem{8} D.Girolami, B.Yadin,Entropy \textbf{19},124 (2017)
  \bibitem{9} J.Baum, M.Munowitz, A.N.Garroway, A.Pines,J.Chem.Phys. \textbf{83}, 2015 (1985)
  \bibitem{10} B. Swingle, G. Bentsen, M. Scheleier-Smith, P. Hayden, Phys.	Rev. A. \textbf{94}, 040302 (2010)
  \bibitem{11} F.M. Cucchietti, J.Opt.Soc. Am. B\textbf{27}, A30 (2010)
  \bibitem{12} I.D. Leroux, M.H. Schleier-Smith, V.Vuletic, Phys.Rev.Lett. \textbf{104}, 073602 (2010)
  \bibitem{13} T.Macri, A. Smerzi, L.Pezze, Phys.Rev. A. \textbf{94}, 010102 (2016)
  \bibitem{14} M.Gartner, J.G.Bohnet, A.Safavi-Naini, M.L. Wall, J.J. Bollinger, A.M.Rey, Nat.Phys. \textbf{13} ,781 (2017)
  \bibitem{15} G.A.Bochkin, S.G.Vasil'ev, S.I. Doronin, E.I.Kuznetsova,I.D.Lazarev,E.B.Fel'dman, Appl.Magn.Reson. \textbf{51},667-678 (2020)
  \bibitem{16} E.B.Fel'dman, A.N. Pyrkov, A.I.Zenchuk, Philos. Trans. R. Soc. London A\textbf{370}, 4690 (2012)
  \bibitem{17} G.B.Furman, V.M.Meerovich, V.L.Sokolovsky, Phys. Rev. A.\textbf{78} 042301 (2008)
  \bibitem{18} M.Goldman. Spin temperature and nuclear magnetic resonance in solids, Oxford,UK, Clarendon Press. 1970.
  \bibitem{19} S.I.Doronin, I.I.Maksimov, E.B.Fel’dman, J. Exp. Theor. Phys.\textbf{91}, 597 (2000)
  \bibitem{20} E.B.Fel'dman, S.Lacelle,Chem.Phys.Lett. \textbf{253}, 27 (1996)
  \bibitem{21} A.Abragam, The Principles of Nuclear Magnetism, Clarendon. Oxford. 1961
  \bibitem{22} J. Baugh, A. Kleinhammes, D. Han, Q. Wang, Y.Wu, Science \textbf{294}, 1505 (2001)
  \bibitem{23} G.A. Bochkin, E.B. Fel'dman, E.B. Kuznetsova, I.D. Lasarev, S.G. Vasil'ev, V.I.Volkov, J. Magn.Reson. \textbf{319}, 106816 (2020)
\end{thebibliography}
